Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-11-28 Docs/IJES/journal.tex
minor changes
including some references

\REF{to this paper should be made as follows: Rodr\'{\i}guez
Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
corporate environmental disclosures on the internet: the case of
IBEX 35 Spanish companies', {\it International Journal of Metadata,
Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}

@@

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed functional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by \cite{Pavlinovic2015}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

@@

%\section*{Acknowledgement}
%The project is funded in part by the National Institutes of Health, under Grant No. 5R01CA136535.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliography{ijmso}
%\bibliographystyle{unsrt}
%\bibliographystyle{alpha}

@@

\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
Myneni, S. and  Patel, V.L. (2010) 'Organization of biomedical data
for collaborative scientific research: a research information
management system', {\it International Journal of Information
Management}, Vol. 30, No. 3, pp.256--264

\bibitem[\protect\citeauthoryear{Bekelman et al.}{2003}]{bekelman03}
Bekelman, J.E., Li, Y. and Gross, C.P. (2003) 'Scope and impact of
financial conflicts of interest in biomedical research: a systematic
review', {\it JAMA}, Vol. 289, No. 19, pp.454--65

\bibitem[\protect\citeauthoryear{Stein}{2008}]{stein08}
Stein, L.D. {2008} 'Towards a cyberinfrastructure for the biological
sciences: progress, visions and challenges', {\it Nature Reviews
Genetics}, Vol. 9, No. 9, pp.678--688.

\bibitem[\protect\citeauthoryear{NIH Statement on Sharing Scientific Research
Data}{http://grants.nih.gov/grants/policy/data\_sharing/}]{nih03datasharing}
NIH Statement on Sharing Scientific Research Data,
http://grants.nih.gov/grants/policy/data\_sharing/

\bibitem[\protect\citeauthoryear{Policy for sharing of data obtained in NIH supported or conducted
genome-wide association studies}{2008}]{nih08policy} Policy for
sharing of data obtained in NIH supported or conducted genome-wide
association studies,
http://grants.nih.gov/grants/guide/notice-files/not-od-07-088.html

>>>>

\REF{\textcolor{red}{to this paper should be made as follows: Rodr\'{\i}guez
Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
corporate environmental disclosures on the internet: the case of
IBEX 35 Spanish companies', {\it International Journal of Metadata,
Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}}

@@

Recently, the SMT solver Z3 has been extended to pose and solve optimization problems modulo theories ~\cite{Bjorner2015}. In particular, 
$\nu$Z tool offers substantial performance improvement in optimization problems~\cite{Bjorner2014,Bjorner2015}. As an application example, \cite{Pavlinovic2015} propose an approach which considers all possible compiler error sources for statically typed fu	nctional programming languages and reports the most useful one subject to some usefulness criterion. The authors formulate this approach as an optimization problem related to SMT and use $\nu$Z to compute an optimal error source in a given ill-typed program. The approach described by \cite{Pavlinovic2015}, which uses MaxSMT solver $\nu$Z, shows a significant performance improvement if compared to previous SMT encodings and localization algorithms.

@@

@@

\bibitem[\protect\citeauthoryear{Arato et al.}{2003}]{Arato2003}
Arato, P., Juhasz, S., Mann, A., Orban, A. and Papp, D. (2003) 'Hardware/software partitioning in embedded system design', {\it Intl. Symp. on Intelligent Signal Processing}, pp.192--202

\bibitem[\protect\citeauthoryear{Mann et al.}{2007}]{Mann2007}
Mann, A., Orban, A. and Arato, P. (2007) 'Finding optimal hardware/software partitions', {\it Formal Methods in System Design}, Vol. 31, No. 3, pp.241--263

\bibitem[\protect\citeauthoryear{Trindade and Cordeiro}{2015}]{Trindade2015}
Trindade, A. and Cordeiro, L. (2015) 'Applying SMT-based verification to hardware/software partitioning in embedded systems', {\it Design Automation for Embedded Systems (to appear)}

\bibitem[\protect\citeauthoryear{Trindade et al.}{2016}]{Trindade2016}
Trindade, A., Ismail, H. and Cordeiro, L. (2016) 'Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper)', {\it V Brazilian Symp. on Computing Systems Engineering (to appear)}

\bibitem[\protect\citeauthoryear{Bjorner et al.}{2015}]{Bjorner2015}
Bjorner, N., Phan, A. and Fleckenstein, L. (2015) 'vZ - An Optimizing SMT Solver', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, Vol. 9035, pp.194--199

\bibitem[\protect\citeauthoryear{Tang et al.}{2010}]{Tang2009}
Tang, T., Lin, Y. and Ren, X. (2010) 'Mapping OpenMP concepts to the stream programming model', {\it Proc. of the Intl. Conf. on Computer Science Education}, pp.1900--1905

\bibitem[\protect\citeauthoryear{Muller}{2002}]{OpenMP1998}
Muller, M. (2002) 'OpenMP Architecture Review Board, OpenMP C and C++ Application Program Interface, Version 2.0', {\it OpenMP Architecture Review Board}

\bibitem[\protect\citeauthoryear{Cordeiro et al.}{2012}]{Cordeiro2012}
Cordeiro, L. Fischer, B. and Marques-Silva, J. (2012) 'SMT-based Bounded Model Checking for Embedded ANSI-C Software', {\it IEEE Transactions on Software Engineering}, Vol. 38, No. 4, pp.957--974

\bibitem[\protect\citeauthoryear{Rao}{2009}]{Rao2009}
Rao, S. (2009) 'Engineering Optimization: Theory and Practice. 4th edition'

\bibitem[\protect\citeauthoryear{Biere et al.}{2009}]{Biere2009}
Biere, A., Heule, M., Maaren, H. and Walsh, T. {2009} 'Bounded Model Checking', {\it Handbook of Satisfiability}

\bibitem[\protect\citeauthoryear{Clarke et al.}{2001}]{Clarke2001}
Clarke, E., Biere, A., Raimi, R. and Zhu, Y. (2001) 'Bounded model checking using satisfiability solving', {\it Formal Methods in System Design}, Vol. 19, No. 1, pp.7--34

\bibitem[\protect\citeauthoryear{Armando et al.}{2009}]{Armando2009}
Armando, A., Mantovani, J. and Platania, L. (2009) 'Bounded model checking of software using SMT solvers instead of SAT solvers', {\it Intl. Journal on Software Tools for Technology Transfer}, Vol. 11, No. 1, pp.69--83

\bibitem[\protect\citeauthoryear{Ganai and Gupta}{2006}]{Ganai2006}
Ganai, M. K. and Gupta, A. (2006) 'Accelerating high-level bounded model checking', {\it Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design}, pp.794--801

\bibitem[\protect\citeauthoryear{Ramalho et al.}{2013}]{Ramalho2013}
Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L. and Fischer, B. (2013) 'SMT-Based Bounded Model Checking of C++ Programs', {\it Intl. Conf. and Workshops on the Engineering of Computer-Based Systems}, pp.147--156

\bibitem[\protect\citeauthoryear{Moura and Bjorner}{2008}]{DeMoura2008}
Moura, L. and Bjorner, N. (2008) 'Z3: An Efficient SMT Solver', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, pp.337--340

\bibitem[\protect\citeauthoryear{Brummayer and Biere}{2009}]{Brummayer2009}
Brummayer, R. and Biere, A. (2009) 'Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays', {\it Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems}, Vol. 5505, pp.174--177

\bibitem[\protect\citeauthoryear{Barrett et al.}{2011}]{Barrett2011}
Barrett, C., Conway, C., Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A. and Tinelli, C. (2011) 'CVC4', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 6806, pp.171--177

\bibitem[\protect\citeauthoryear{Bozzano et al.}{2005}]{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S. and Sebastiani, R. (2005) 'MathSAT: Tight integration of SAT and mathematical decision procedures', {\it Journal of Automated Reasoning}, Vol. 35, No. 1-3, pp.265--293

\bibitem[\protect\citeauthoryear{Dutertre}{2014}]{Dutertre2014}
Dutertre, B. (2014) 'Yices 2.2', {\it Proc. of the Intl. Conf. on Computer-Aided Verification}, Vol. 8559, pp.737--744

\bibitem[\protect\citeauthoryear{Wu et al.}{2014}]{Wu2014}
Wu M., Wu, W., Tai, N., Zhao, H., Fan, J. and Yuan, N. (2014) 'Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP', {\it Proc. of the Intl. Conf. on Software Engineering and Service Science}, pp.921--924

\bibitem[\protect\citeauthoryear{Bjorner and Phan}{2014}]{Bjorner2014}
Bjorner, N. and Phan, A (2014) 'vZ - Maximal Satisfaction with Z3', {\it Proc. of the Intl. Symp. on Symbolic Computation in Software Science}, pp.1--10

\bibitem[\protect\citeauthoryear{Paci et al}{2008}]{Federica2008}
Paci, F., Ferrini, R., Sun, Y. and Bertino, E. (2008) 'Authorization and User Failure Resiliency for WS-BPEL business processes', {\it Proc. of the Intl. Conf. on Service-Oriented Computing}, pp.116--131

\bibitem[\protect\citeauthoryear{Narodytska and Bacchus}{2014}]{NarodytskaN}
Narodytska, N. and Bacchus, F. (2014) 'Maximum Satisfiability Using Core-Guided MAXSAT Resolution', {\it Proc. of the Conf. on Artificial Intelligence}, pp.2717--2723
